\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{merriweather}
\usepackage[hidelinks]{hyperref}

\title{\textbf{
CS213 - Software Systems Lab \\ 
Project Proposal: VaxiN O'pandemic
}}
\author{
  B Siddharth Prabhu\\
  \href{mailto:200010003@iitdh.ac.in}{\texttt{200010003@iitdh.ac.in}}
  \and
  Ishika Sharma\\
  \href{mailto:200010020@iitdh.ac.in}{\texttt{200010020@iitdh.ac.in}}
  \and
  Nirmit Arora\\
  \href{mailto:200010034@iitdh.ac.in}{\texttt{200010034@iitdh.ac.in}}
}
\date{September 17, 2021}

\begin{document}

\maketitle

\section{Introduction and Motivation}
In these unprecedented times, we can't neglect the effects of the pandemic, and must speed up the process of vaccination. So, using our knowledge of Software Systems Lab, we decided to develop a portal to aid the drive.

\section{Main Tasks and Goals}
\begin{itemize}
    \item Login and Sign-Up (via phone no.) %some methods like otp
    \item Information and Awareness
    \item Statistics % using python
    \item Map of Cases and Vaccine coverage % dynamically updating
    \item Slot availability
    \begin{itemize}
        \item Vaccine dose type
        \item Age groups
        \item Locations
        \item If private, then fee
    \end{itemize}
    \item Other Eligibility Criteria
    \item Certificate of Vaccination (Generation and download/ printable HTML page)
    \item ...and more, perhaps!
    % \item Login and Sign-Up (Student, Admin, Staff)
    % \item Assignments, Quizzes
    % \item Discussion Forums
    % \item Course Management
    % \item Marking and Grading
    % \item Events and Notifications
    % \item Feedback Form
    % \item Lectures/Resources of NPTEL/etc.
\end{itemize}

\section{Justification}
\begin{itemize}
    \item HTML/CSS will be used in the website's display features.
    \item Javascript and PHP will be used to validate/process form input.
    \item SQL will be used to manage a database of the information.
    \item \LaTeX~and beamer will be used to maintain documentation and reports
    \item Python will be used for statistics.
    \item Git will be used for version control.
\end{itemize}

\end{document}
